---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ccweedmetapkg

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of ccweedmetapkg is to provide easy access (for R users) to data associated with the the publication XX. This dataset has been published using Iowa State University's DataShare program and can also be accessed via [this]() link. Because the dataset is published elsewhere, readers/users to directed to the DataShare website for detailed data descriptions. 

## Installation

You can install the github version of the package using the following code:

``` r
devtools::install_github("vanichols/ccweedmetapkg")
```
## Data

You are in luck - there is only one dataset associated with this package: **ccweeddat**
This is a basic example which shows you how to solve a common problem:

```{r example}
library(ccweedmetapkg)
ccweeddat %>% summary()
```
